
\begin{thebibliography}{88} % assuming between 10 and 99 references

 \bibitem{chorin1968numerical} Chorin, Alexandre Joel. "Numerical solution of the Navier-Stokes equations." Mathematics of computation 22.104 (1968): 745-762.

 \bibitem{key2} Chorin, Alexandre Joel, and Jerrold E. Marsden. A mathematical introduction to fluid mechanics. Vol. 3. New York: Springer, 1990.

 \bibitem{key3} Brown, David L., Ricardo Cortez, and Michael L. Minion. "Accurate projection methods for the incompressible Navier–Stokes equations." Journal of Computational Physics 168.2 (2001): 464-499.

 \bibitem{key4} A. S. Almgren, J. B. Bell, and W. G. Szymczak, A numerical method for the incompressible Navier–Stokes equations based on an approximate projection, SIAM J. Sci. Comput. 17(2), (1996).

 \bibitem{key5} A. S. Almgren, J. B. Bell, and W. Y. Crutchfield, Approximate projection methods. 1. Inviscid analysis, SIAM J. Sci. Comput. 22(4), (2000).

 \bibitem{key6} Temam, Roger. Navier-Stokes equations and nonlinear functional analysis. Vol. 66. Siam, 1995.
 
 \bibitem{key7} Maria Denaro, Filippo. "On the application of the Helmholtz–Hodge decomposition in projection methods for incompressible flows with general boundary conditions." International Journal for Numerical Methods in Fluids 43.1 (2003): 43-69.

 \bibitem{key8} Johnston, Hans, and Jian-Guo Liu. ``Finite difference schemes for incompressible flow based on local pressure boundary conditions.'' Journal of Computational Physics 180.1 (2002): 120-154.

 \bibitem{key9} 

 \bibitem{key10} 
 
 \bibitem{key11} Harlow, Francis H., and J. Eddie Welch. "Numerical calculation of time-dependent viscous incompressible flow of fluid with free surface." Physics of fluids 8.12 (1965): 2182.

 \bibitem{key12} Howell, Louis H., and John B. Bell. "An adaptive mesh projection method for viscous incompressible flow." SIAM Journal on Scientific Computing 18.4 (1997): 996-1013.

 \bibitem{key13} Bell, John B., Phillip Colella, and Harland M. Glaz. "A second-order projection method for the incompressible Navier-Stokes equations." Journal of Computational Physics 85.2 (1989): 257-283.

 \bibitem{key14} Kim, John, and Parviz Moin. "Application of a fractional-step method to incompressible Navier-Stokes equations." Journal of computational physics 59.2 (1985): 308-323.

 \bibitem{key15} R. Temam, Sur l’approximation de la solution des e´quations de Navier–Stokes par la me´thode des pas fractionnaires ii, Arch. Ration. Mech. Anal. 33 (1969) 377–385.
 
 \bibitem{key16} J. Shen, On error estimates of the projection methods for the Navier–Stokes equations: first-order schemes, SIAM J. Numer. Anal. 29 (1992) 57–77.
 
 \bibitem{key17} Fujita, Hiroshi, and Tosio Kato. "On the Navier-Stokes initial value problem. I." Archive for rational mechanics and analysis 16.4 (1964): 269-315.
 
 \bibitem{key18} Lal, Mindy Fruchtman, Mindy Frucbtman Lai, and Mindy Fruchtman. "~. A Projection Method for Reacting Flow in the Zero Mach Number Limit." (1993).
 
 \bibitem{key19} Minion, Michael L. "A projection method for locally refined grids." Journal of Computational Physics 127.1 (1996): 158-178.
 
 \bibitem{key20} Rannacher, Rolf. On Chorin's projection method for the incompressible Navier-Stokes equations. Springer Berlin Heidelberg, 1992.
 
 \bibitem{key21} R. Temam, Remark on the pressure boundary condition for the projection method, Theoret. Comput. Fluid Dynam. 3, 181 (1991).
 
 \bibitem{key22} W. E and J. Guo Liu, Projection method II. Godunov–Ryabenki analysis, SIAM J. Numer. Anal. 33, 1597 (1996).
 
 \bibitem{key23} J. Shen, On error estimates of the projection methods for the Navier–Stokes equations: Second-order schemes, Math. Comput. 65, 1039 (1996).
 
\end{thebibliography}